Computer Science House Constitution

### 2025-05-24 constitution.tex
updated amendment so that it includes any change to article 9, in accordance with RIT policy or NY law can be treated as a nonsemantic change
voting member clarifications

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
	      The Selections Committee reviews applications in accordance with the process prescribed by ResLife.
	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

@@

The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
	\item Attend at least one CSH social event during the Intro Process
	\item Attend at least two Technical Seminars during the Intro Process
\end{enumerate}

@@

\asubsection{Constitutional Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent of the Eligible Votes.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.

>>>>

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

@@

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}

@@

\asubsection{Constitutional Maintainer Selection}
Any member may nominate a qualified member for Maintainer status to E-Board for consideration.
E-Board may choose to approve or reject the nomination by E-Board Vote with a quorum of seventy-five percent.

@@

\asubsection{Eligible Votes}
The number of Active Members who are eligible to vote on the issue.
Following the first Intro Eval of the academic year, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.
